The interactions of rational, pragmatic agents  \n lead to efficient language structure and use

### 2019-05-11 paper/paper.Rmd
de-anonymized for psycharxiv
reviewer 3 edits

output: cogsci2016::cogsci_paper
---

@@

Importantly, we assume that events $e = <u, m, c>$ are sampled according the to following generative model -- some context occurs in the world with probability $P(C=c)$. Within this context, an object $m$ occurs with probability $p(m|c)$. The speaker attempts to refer to that object by sampling from her conditional distribution $S(u|m, c; \ell)$ (i.e. $e \sim p(c)p(m|c)S(u|m, c; \ell)$). From these ingredients it is possible to derive the following objective between the speaker and listener distributions (see \href{https://bit.ly/2RBSGcU}{SI 2.1} for complete derivation).
\begin{equation}
\begin{split}
  = \mathbb{E}_{c \sim P(C)}[H_{cross}(P_{speaker}, P_{listener} | c; \ell)]\\
\end{split}
\end{equation}
From an information-theoretic perspective this objective is intuitive: $H_{cross}$ denotes the Cross-Entropy (CE), a measure of dissimilarity between two distributions -- the average number of bits required to communicate under one distribution, given that the “true” distribution differs. In our case, we have an expectation over this term -- the expected difference between the distributions assumed by the speaker $P_{speaker}$ and listener $P_{listener}$ given a set of contexts $C$\footnote{Note that in the single context case $|C|=1$ this objective is simply the speaker-listener Cross-Entropy.}. In other words, an "efficient" language $\ell$ minimizes the distance between what speakers and listeners think.

@@

As an example, say we have two objects ($m_1$ and $m_2$), two utterances ($u_1$ and $u_2$), differing in cost, and two languages ($\ell_1$ and $\ell_2$), describing different utterance-meaning mappings. In language $\ell_1$, the low-cost $u_1$ can be used to refer to both $m_1$ and $m_2$ ($[[u_1]]_{\ell_1} = \{m_1, m_2 \}$), but the high-cost $u_2$ cannot be used at all ($[[u_2]]_{\ell_1} = \emptyset$). By contrast, in language $\ell_2$, $u_1$ can only refer to $m_1$ and $u_2$ can only refer to $m_2$ ($[[u_1]]_{\ell_2} = \{m_1\}$ and $[[u_2]]_{\ell_2} = \{m_2 \}$). While it is cheaper for a speaker to use $\ell_1$ (because speaking is always low-cost), it is more difficult for a listener (because $u_1$ is ambiguous). Crucially, however, if context is disambiguating then the speaker can use $u_1$ to refer to either $m_1$ or $m_2$ and $\ell_1$ should be preferred to $\ell_2$.\par

>>>>

output: cogsci2016::cogsci_paper
final-submission: \cogscifinalcopy
---

@@

Importantly, we assume that events $e = <u, m, c>$ are sampled according to the following generative model -- some context occurs in the world with probability $P(C=c)$. Within this context, an object $m$ occurs with probability $p(m|c)$. The speaker attempts to refer to that object by sampling from her conditional distribution $S(u|m, c; \ell)$ (i.e. $e \sim p(c)p(m|c)S(u|m, c; \ell)$). From these ingredients it is possible to derive the following objective between the speaker and listener distributions (see \href{https://bit.ly/2RBSGcU}{SI 2.1} for complete derivation).
\begin{equation}
\begin{split}
  = \mathbb{E}_{c \sim P(C)}[H_{cross}(P_{speaker}, P_{listener} | c; \ell)]\\
\end{split}
\end{equation}
From an information-theoretic perspective this objective is intuitive: $H_{cross}$ denotes the Cross-Entropy (CE), a measure of dissimilarity between two distributions -- the average number of bits required to communicate under one distribution, given that the “true” distribution differs. In our case, we have an expectation over this term -- the expected difference between the distributions assumed by the speaker $P_{speaker}$ and listener $P_{listener}$ given a set of contexts $C$\footnote{Note that in the single context case $|C|=1$ this objective is simply the speaker-listener Cross-Entropy.}. In other words, an "efficient" language $\ell$ minimizes the distance between what speakers and listeners think.

@@

As an example, say we have two objects ($m_1$ and $m_2$), two utterances ($u_1$ and $u_2$), differing in cost, and two languages ($\ell_1$ and $\ell_2$), describing different utterance-meaning mappings. In language $\ell_1$, the low-cost $u_1$ can be used to refer to both $m_1$ and $m_2$ ($[[u_1]]_{\ell_1} = \{m_1, m_2 \}$), but the high-cost $u_2$ cannot be used at all ($[[u_2]]_{\ell_1} = \emptyset$). By contrast, in language $\ell_2$, $u_1$ can only refer to $m_1$ and $u_2$ can only refer to $m_2$ ($[[u_1]]_{\ell_2} = \{m_1\}$ and $[[u_2]]_{\ell_2} = \{m_2 \}$). While it is cheaper for a speaker to use $\ell_1$ (because speaking it is always lower cost), it is more difficult for a listener (because $u_1$ is ambiguous). Crucially, however, if context is disambiguating then the speaker can use $u_1$ to refer to either $m_1$ or $m_2$ and $\ell_1$ should be preferred to $\ell_2$.\par
